---
title: "Plotting"
tutorial:
  id: "plotting"
output:
  learnr::tutorial:
    css: css/style.css
    progressive: true
    allow_skip: true
    theme: flatly
    ace_theme: tomorrow_night_blue
runtime: shiny_prerendered
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE, context="server"}
library(learnr)
library(Pmetrics)
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)
wd<-tempdir()
setwd(wd)

exData <- dataEx
mod1 <- modEx
exFit <- PM_fit$new(model = modEx, data = dataEx)
exRes <- NPex
```

# Introduction

This tutorial will focus on exploring the plotting methods exported by the diferent R6 objects we have seen this far: [`PM_model`](https://lapkb.github.io/Pmetrics/reference/PM_model.html), [`PM_data`](https://lapkb.github.io/Pmetrics/reference/PM_data.html) and [`PM_result`](https://lapkb.github.io/Pmetrics/reference/PM_result.html). Each method seen here will link to their specific documentation page, there you can look at the different parameters that can be passed to the function to personalize the plots.

# Regarding PM_result objects

Through the following sections of this tutorial we will be using `PM_model`, `PM_data` and `PM_result` objects. It is key to notice that the model an data objects can be also accessed through the result object like this:

```{r echo = T, eval = F}
#This
exData$plot()
#Is equivalent to this
exRes$data$plot()
```

Also notice that altough they are equal objects, they are not the same object (modifications on one of the objects will not be reflected on the other one)

## Plotting PM_model

As seen in the [model builder app](https://lapkb.github.io/Pmetrics/reference/build_model.html), `PM_model` objects can be [plotted](https://lapkb.github.io/Pmetrics/reference/plot.PM_model.html).

```{r summary_model, exercise = TRUE}
modEx
```

```{r plot_model, exercise = TRUE}
modEx$plot()
```

In this case, the model is analytic so Pmetrics will infer its compartmental structure based on the names of the primary parameters.

## Plotting PM_data

Plot the raw data using R6 with various options. Type `?plot.PM_data` in the R console for [help](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html).

```{r plot_1, exercise = TRUE}
exRes$data$plot()
```

Now, you try plotting the same PM_data object but only between hours 120-145. Remember checking the [documentation](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html)

```{r exerc_plot_1, exercise = TRUE}

```

```{r exerc_plot_1-solution}
exRes$data$plot(xlim = c(119, 145))
```



A very useful diagnostic plot is to compare the individual observations of each subject with their correspondent posterior profiles. Look at the [documentation](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html).

```{r plot_PM_data_question, echo = FALSE}
question("Which specific arguments do you think might be useful to generate the plot described above?",
          answer("include"),
          answer("line", correct = TRUE),
          answer("marker"),
          answer("names"),
          answer("log"),
          answer("overlay", correct = TRUE),
          allow_retry = TRUE
)
```

How would you generate that plot?

```{r data_pred_plot, exercise = TRUE}

```

```{r data_pred_plot-solution}
exRes$data$plot(overlay=F,line=list(pred=exRes$post))
```



In this case, as we want individual plots for each subject `overlay` must be set to False and because we want to plot the posterior predictions we pass the `exRes$post` object to the `Line` argument.

Now, how would you plot all observations in a single plot with the population predictions?

How would you generate that plot?

```{r data_pred_pop_plot, exercise = TRUE}

```

```{r data_pred_pop_plot-solution}
exRes$data$plot(line=list(pred=exRes$pop))
```

<!-- exRes$data$plot(line = list(join = F, pred = exRes$post),marker = list(color = "blue", symbol = 2)) -->


## Observed vs Predicted

[PM_op](https://lapkb.github.io/Pmetrics/reference/PM_op.html) objects can be accessed vía the `$op` attribute of [PM_result](https://lapkb.github.io/Pmetrics/reference/PM_result.html) objects.

This object exposes some methods, but for the moment we will focus on the `$plot()` one.
Type `?plot.PM_op` in the R console for help.

```{r}
exRes$op$plot()
exRes$op$plot(pred.type = "pop")
exRes$op$plot(line = list(lm = list(ci = .9, color = "red"), loess = F))
```

The PM_op object can be disaggregated into a Tidy compatible format using the `$data` field, see [tidyverse](https://www.tidyverse.org/).

```{r}
library(tidyverse)
exRes$op$data %>%
plot()
exRes$op$data %>%
filter(pred > 5) %>%
filter(pred < 10) %>%
plot()
```

The original op object data can always be accessed via `exRes$op$data`

Try using the `head()` function and the pipe operator `%>%` to print the first 10 rows of the op object.

```{r head_op, exercise = TRUE}

```

```{r head_op-solution}
exRes$op$data %>% head(10)
```



PM_op also exposes other useful methods like `$summary`:

```{r}
exRes$op$summary(pred.type = "pop")
exRes$op$summary(icen = "mean")
```

?summary.PMop for help

## PM_final

`PM_final$plot()` is used to plot the final population joint density. Type [?plot.PMfinal](https://lapkb.github.io/Pmetrics/reference/plot.PM_final.html) in
the R console for help.

The [PM_final](https://lapkb.github.io/Pmetrics/reference/PM_final.html) object is exposed by the `PM_result$final` attribute.

```{r}
exRes$final$plot()
```

Add a kernel density curve to the final plot:

```{r density_final_plot, exercise = TRUE}

```

```{r density_final_plot-solution}
exRes$final$plot(density=T)
```



This function can also generate bivariate plots by supplying the appropiate formulate using the R syntax `x~y`:

```{r}
exRes$final$plot(Ke~V,
  marker = list(
    color = "red",
    symbol ="diamond"
  ),
  line = list(
    color = "purple",
    dash = "dash", width = 2
  )
)
```

As with the previous example, the original tidy-compatible object can be accessed through the `$data` attribute.

```{r}
exRes$final$data$popPoints
```

This object contains useful information about the final non-parametric distribution of the parameters and their relevant statistics, we again invite you to look at the diferent options available in the [documentation](https://lapkb.github.io/Pmetrics/reference/PM_final.html)

```{r}
exRes$final$summary()
```

## PM_cycle

The [`PM_cycle`](https://lapkb.github.io/Pmetrics/reference/PM_cycle.html) object stores the information of the fitting process cycle-by-clycle. Things like the -2LL, Gamma/Lambda or evolution of the different parameters'statistics can be found in this object.

Before showing the plotting function, it is important to realize that given the nature of the diverse data within this object, it might be possible that the general plot provided by Pmetrics might not necessarily fulfill your needs. By knowing where and how the data is stored, you can easily pull the specific data you need and plot it as you see fit.

```{r}
exRes$cycle$plot()
```

As expected this plot is giving us a general overview of the fitting process through the cycles.
Expecific elements can be accessed through the `$data` attribute.
like:

```{r}
exRes$cycle$data$ll %>% head()
```

or:

```{r}
exRes$cycle$data$mean %>% head()
```

======ALL BELOW THIS LINE IS WORK IN PROGRESS======

## PM_cov

This is the final object we will be learning about in this tutorial. This said, there are more plotting functionalities included for other objects in the package, but we will be reviewing those as we learn how to interact with those specific objects.

The [`PM_cov`](https://lapkb.github.io/Pmetrics/reference/PM_cov.html) object contains all the information related to covariates and the relation with the primary models for the final bayesian posterior.

Again, as in the bimodal plots for PM_final, we need to supply a plotting formulate in the R form `x~y`:

```{r}
exRes$cov$plot(V~wt)
```

Now is your turn, generate the same plot but with mean Bayesian posterior parameter values.

```{r cov_icen_mean, exercise = TRUE}

```

```{r cov_icen_mean-solution}
exRes$cov$plot(V~wt,icen ="mean")
```



`PM_cov` objects also provide a tidy-compatible structure that can be operated over:

```{r}
exRes$cov$data |>
filter(age>25) |>
plot(V ~ wt)
```

There are also more advance plots that can be done using `PM_cov$plot()`. Remember looking at the [documentation](https://lapkb.github.io/Pmetrics/reference/plot.PM_cov.html).

```{r}
exRes$cov$plot(Ke ~ age, lowess = F, reg = T, pch = 3)
```

When time is the x variable, the y variable is aggregated by subject. In
R plot formulae, calculations on the fly can be included using the I()
function:

```{r}
exRes$cov$plot(I(V*wt) ~ time)
```

<!-- Look at all possible covariate-parameter relationships by multiple
linear regression with forward and backward elimination - type `?PMstep`
in the R console for help.
exRes$step() icen works here too.... exRes$step(icen = "median") forward
elimination only exRes\$step(direction = "forward") -->
