---
title: "Plotting"
tutorial:
  id: "plotting"
output:
  learnr::tutorial:
    css: css/style.css
    progressive: true
    allow_skip: true
    theme: flatly
    ace_theme: tomorrow_night_blue
runtime: shiny_prerendered
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE, context="server"}
library(learnr)
library(Pmetrics)
library(tidyverse)
library(gradethis)
gradethis::gradethis_setup()
knitr::opts_chunk$set(echo = TRUE)
wd<-tempdir()
setwd(wd)

exData <- PM_data$new("Examples/src/ex.csv")
mod1 <- PM_model$new("Examples/src/model.txt")
exFit <- PM_fit$new(model = mod1, data = exData)
exRes <- NPex
```

# Introduction

This tutorial will focus on exploring the plotting methods exported by the diferent R6 objects we have seen this far: [`PM_model`](https://lapkb.github.io/Pmetrics/reference/PM_model.html), [`PM_data`](https://lapkb.github.io/Pmetrics/reference/PM_data.html) and [`PM_result`](https://lapkb.github.io/Pmetrics/reference/PM_result.html). Each method seen here will link to their specific documentation page, there you can look at the different parameters that can be passed to the function to personalize the plots.

# Regarding PM_result objects

Through the following sections of this tutorial we will be using `PM_model`, `PM_data` and `PM_result` objects. It is key to notice that the model an data objects can be also accessed through the result object like this:

```{r echo = T, eval = F}
#This
exData$plot()
#Is equivalent to this
exRes$data$plot()
```

Also notice that altough they are equal objects, they are not the same object (modifications on one of the objects will not be reflected on the other one)

## Plotting PM_model

As seen in the [model builder app](https://lapkb.github.io/Pmetrics/reference/build_model.html), `PM_model` objects can be [plotted](https://lapkb.github.io/Pmetrics/reference/plot.PM_model.html).

```{r summary_model, exercise = TRUE}
modEx
```

```{r plot_model, exercise = TRUE}
modEx$plot()
```

In this case, the model is analytic so Pmetrics will infer its compartmental structure based on the names of the primary parameters.

## Plotting PM_data

Plot the raw data using R6 with various options. Type `?plot.PM_data` in the R console for [help](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html).

```{r plot_1, exercise = TRUE}
exRes$data$plot()
```

Now, you try plotting the same PM_data object but only between hours 120-145. Remember checking the [documentation](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html)

```{r exerc_plot_1, exercise = TRUE}

```

```{r exerc_plot_1-solution}
exRes$data$plot(xlim = c(119, 145))
```

<!-- ```{r exerc_plot_1-code-check}
gradethis::grade_this_code()
``` -->

A very useful diagnostic plot is to compare the individual observations of each subject with their correspondent posterior profiles. Look at the [documentation](https://lapkb.github.io/Pmetrics/reference/plot.PM_data.html).

```{r plot.PM_data_question}
question("Which specific arguments do you think might be useful to generate the plot described above?",
          answer("include"),
          answer("line", correct = TRUE),
          answer("marker"),
          answer("names"),
          answer("log"),
          answer("overlay", correct = TRUE),
          allow_retry = TRUE
)
```

How would you generate that plot?

```{r data_pred_plot, exercise = TRUE}

```

```{r data_pred_plot-solution}
exRes$data$plot(overlay=F,line=list(pred=exRes$post))
```

<!-- ```{r data_pred_plot-code-check}
gradethis::grade_this_code()
``` -->

In this case, as we want individual plots for each subject `overlay` must be set to False and because we want to plot the posterior predictions we pass the `exRes$post` object to the `Line` argument.

Now, how would you plot all observations in a single plot with the population predictions?

How would you generate that plot?

```{r data_pred_pop_plot, exercise = TRUE}

```

```{r data_pred_pop_plot-solution}
exRes$data$plot(line=list(pred=exRes$pop))
```

<!-- exRes$data$plot(line = list(join = F, pred = exRes$post),marker = list(color = "blue", symbol = 2)) -->
<!-- ```{r data_pred_pop_plot-code-check}
gradethis::grade_this_code()
``` -->

## Observed vs Predicted Plots

======ALL BELOW THIS LINE IS WORK IN PROGRESS======

<!-- The following are the older S3 method with plot(...) for the first two
examples You can use R6 or S3 for any Pmetrics object We will focus on
R6 as the more modern way. plot(exRes$data) plot(exRes$data, xlim =
c(119, 146), marker = list(color = "blue"))

here's a summary of the original data file; ?summary.PM_data for help
exRes$data$summary() -->

Plot some observed vs. predicted data. Type ?plot.PM_op in the R console
for help. exRes$op$plot() exRes$op$plot(pred.type = "pop")
exRes$op$plot(line = list(lm = list(ci = .9, color = "red"), loess = F))

The OP plot can be disaggregated into a Tidy compatible format using the
$data field (see https://www.tidyverse.org/) library(tidyverse) exRes$op$data %>% plot() exRes$op\$data
%\>% filter(pred \> 5) %\>% filter(pred \< 10) %\>% plot()

the original op object data can be accessed via exRes$op$data

see a header with the first 10 rows of the op object head(exRes$op$data, 10)

get a summary with bias and imprecision of the population predictions;
?summary.PMop for help exRes$op$summary(pred.type = "pop")

the S3 way summary(exRes\$op, pred.type = "pop")

look at the summary for the posterior predictions (default pred.type)
based on means of parameter values exRes$op$summary(icen = "mean")

Plot final population joint density information. Type ?plot.PMfinal in
the R console for help. exRes$final$plot()

add a kernel density curve exRes$final$plot(density = T)

A bivariate plot. Plotting formulae in R are of the form 'y\~x'
exRes$final$plot(Ke \~ V, marker = list(color = "red", symbol =
"diamond"), line = list(color = "purple", dash = "dash", width = 2) )

or the S3 way plot(exRes\$final)

The original final object can be accessed using exRes$final$data
names(exRes$final$data)

see the population points exRes$final$popPoints

or exRes$final$data\$popPoints

see the population mean parameter values exRes$final$popMean

see a summary with confidence intervals around the medians and the
Median Absolute Weighted Difference (MAWD); ?summary.PMfinal for help
exRes$final$summary()

Plot cycle information Type ?plot.PMcycle in the R console for help.
exRes$cycle$plot()

names of the cycle object; ?makeCycle for help names(exRes$cycle$data)

gamma/lamda value on last 6 cycles tail(exRes$cycle$data\$gamlam)

Plot covariate information. Type ?plot.PMcov in the R console for help.
Recall that plotting formulae in R are of the form 'y\~x'
exRes$cov$plot(V \~ wt) exRes$cov$data %\>% plot(V \~ wt) exRes$cov$data
%\>% filter(age \> 25) %\>% plot(V \~ wt)

exRes$cov$plot(Ke \~ age, lowess = F, reg = T, pch = 3)

Same plot but with mean Bayesian posterior parameter and covariate
values... Remember the 'icen' argument? exRes$cov$plot(V \~ wt, icen =
"mean")

When time is the x variable, the y variable is aggregated by subject. In
R plot formulae, calculations on the fly can be included using the I()
function exRes$cov$plot(I(V \* wt) \~ time)

The previous cov object can be seen via: exRes\$cov

but to access individual elements, use: exRes$cov$data[, 1:3] for
example names(exRes\$cov)

summarize with mean covariates; ?summary.PM_cov for help
exRes$cov$summary(icen = "mean")

Look at all possible covariate-parameter relationships by multiple
linear regression with forward and backward elimination - type ?PMstep
in the R console for help.
exRes$step() icen works here too.... exRes$step(icen = "median") forward
elimination only exRes\$step(direction = "forward")
